### 2018-06-22 Thesis/Parts/Conclusion/Conclusion.tex
Journal plot
discussion & presentation

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Conclusion}
This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives for our categorization task, based on article titles. The TF-IDF alternatives give better results than the embeddings based on abstracts. The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level, although this improvement cannot be seen as significant on our dataset. This improved embedding results in a median rank decrease of 8 on the titles and an median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.  The embedding also results in a memory decrease of 73.04\% compared to the best performing TF-IDF alternative, making it more viable to keep it in memory. We thus come to the following conclusions:
\begin{enumerate}
\item{Article based embeddings perform better than TF-IDF on titles, small texts, which contain limited information}
\item{TF-IDF performs better than article based embeddings on abstracts, larger texts, which contain more information}
\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
\end{enumerate}
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Conclusion}
This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives on our categorization task, based on article titles. The TF-IDF alternatives give better results than the embeddings based on abstracts. The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level, although this improvement cannot be seen as significant on our dataset. This improved embedding set results in a median rank decrease of 8 on the titles and an median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.  The embedding also results in a memory decrease of 73.04\% compared to the best performing TF-IDF alternative, making it more viable to keep it in memory. The visualization of the journal embedding show that similar journals are grouped together, indicating a preservation of relatedness between the journal embeddings. We thus come to the following conclusions:
\begin{enumerate}
\item{Article based embeddings perform better than TF-IDF on titles, small texts, which contain limited information}
\item{TF-IDF performs better than article based embeddings on abstracts, larger texts, which contain more information}
\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
\item{Visualization of the journal embeddings show that the embeddings capture and preserve subject relatedness when they are combined to create embeddings for larger texts}

\end{enumerate}
\end{document}

### 2018-06-22 Thesis/Parts/Discussion/Discussion.tex
discussion & presentation

\documentclass[../../Thesis.tex]{subfiles}
\externaldocument{../Research_results/Research_results}
\externaldocument{../Data/Data}
\begin{document}
\header{Discussion}
\subheader{Best performers}
The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on title. For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.
\subheader{Sets}
\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title. The main difference between the abstract \& title is that the title contains less tokens (see table~\ref{table:corpusSize}), this means that the titles contain less information. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles. The TF-IDF method works better on the abstract, which contain more tokens, which improves the differentiating the different abstract. The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case. It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not looked into this further due to our findings that the TF-IDF performance stagnates (presented in figure~\ref{figure:tfidfPerformance}).
\subsubheader{Embedding}
\subsubsubheader{Limited tfidf embeddings}
The limited TF-IDF embeddings all under perform, compared to the non-limited TF-IDF embedding, on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results, higher vocabulary sizes give better performance. However, figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. Their pattern show a decent performance indicates the following pattern: a high/average performance on the top-rankings, an under performance on the middle rankings and  a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that is did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the high end of the rankings, or the lower end. Resulting in low median and average scores, but in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and/or abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However they can be processed more efficiently during calculations}. This results in a lower memory requirement.

@@

\subheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in figure~\ref{figure:tfidfPerformance}). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is significantly worse than the embedding, which also uses less memory.

\subheader{Journal plots}
Figure~\ref{figure:journalPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figure~\ref{figure:journalPlotGroups} shows the journals, grouped with k-means on the original 300-dimensional embedding vector. On the bottom right hand side, the journals closest to the center point of the k-means algorithm are displayed. In this plot we can see that the original embedding-clustering is relatively well preserved, most groups stay clustered together. The central journals belong to mainly mixed groups, which is likely caused by either their general nature, or due to a collection of articles on the opposing ends of the spectrum.\\
The interactive version shows that the clusterings, as seen on both figure~\ref{figure:journalPlotNormal} \&~\ref{figure:journalPlotGroups} are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates.
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\externaldocument{../Research_results/Research_results}
\externaldocument{../Data/Data}
\begin{document}
\header{Discussion}

\subheader{Result analysis}
\subsubheader{Best performers}
The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on title. For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.

\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title. The main difference between the abstract \& title is that the title contains less tokens (see table~\ref{table:corpusSize}), this means that the titles contain less information. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles. The TF-IDF method works better on the abstract, which contain more tokens, which improves the differentiating the different abstract. The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case. It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not looked into this further due to our findings that the TF-IDF performance stagnates (presented in figure~\ref{figure:tfidfPerformance}).

\subsubheader{Limited tfidf embeddings}
The limited TF-IDF embeddings all under perform, compared to the non-limited TF-IDF embedding, on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results, higher vocabulary sizes give better performance. However, figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. Their pattern show a decent performance indicates the following pattern: a high/average performance on the top-rankings, an under performance on the middle rankings and  a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that is did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the high end of the rankings, or the lower end. Resulting in low median and average scores, but in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and/or abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However they can be processed more efficiently during calculations}. This results in a lower memory requirement.

@@

\subsubheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in figure~\ref{figure:tfidfPerformance}). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is significantly worse than the embedding, which also uses less memory.

\subsubheader{Journal plots}
Figure~\ref{figure:journalPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figure~\ref{figure:journalPlotGroups} shows the journals, grouped with k-means on the original 300-dimensional embedding vector. On the bottom right hand side, the journals closest to the center point of the k-means algorithm are displayed. While most journal titles clearly state the research field, some do not. SAGE opens research area is social and behavioural sciences and humanities, RSC Advances' research area is chemical sciences and Orvosi hetilaps research area is experimental and clinical medicine. In the plot we can see that the original embedding-clustering is relatively well preserved, most groups stay clustered together. The central journals belong to mainly mixed groups, which is likely caused by either their general nature, or due to a collection of articles on the opposing ends of the spectrum.\\
The interactive version shows that the clusterings, as seen on both figure~\ref{figure:journalPlotNormal} \&~\ref{figure:journalPlotGroups} are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates. We found that our findings on the 2-dimensional representation of embeddings are simmilar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.

\subheader{Improvements}
This research shows that, even tough the embeddings are able to capture and preserve relatedness, TF-IDF is able outperform the embeddings. Earlier research already proposed improvements to the word embeddings.
\citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the wikipedia corpus, and a 3.9\% improvement on the same task based on the arXiv articles. Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative. While this looks promising, we have to keep in min that our task differs from earlier tasks, since we do not categorize on 2 categories, but on more than 3k. Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale.

\end{document}

### 2018-06-22 Thesis/Parts/Future_work/Future_work.tex
discussion & presentation

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
This research focussed on the quality of word embeddings on academic texts. To do this we used both a comparison to TF-IDF and a visualization of the word embeddings. Future works may seek to further improve the quality of the word embeddings. 
\subheader{Smarter cutting}
An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings. This might be achieved by analysing the word embedding spectrum before normalization, and to then cut the center of the vector space out. This must be applied before normalization, since normalization causes all embeddings to have a distance of 1 to the center point. All words which are generic are in the center of the spectrum. Removing these words prevents the larger texts to be pulled towards the middle, where they lose the parts of their meaning which sets them apart from the other journals. We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
This research focussed on the quality of word embeddings on academic texts. To do this we used both a comparison to TF-IDF and a visualization of the word embeddings. Future works may seek to further improve the quality of the word embeddings.

\subheader{Intelligent cutting}
An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings. This might be achieved by analysing the word embedding spectrum before normalization, and to then cut the center of the vector space out. This must be applied before normalization, since normalization causes all embeddings to have a distance of 1 to the center point. All words which are generic are in the center of the spectrum. Removing these words prevents the larger texts to be pulled towards the middle, where they lose the parts of their meaning which sets them apart from the other journals. We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.
